Post-Disturbance Tree Community Trajectories in a Neotropical Forest

### 2018-04-23 WholePlotTrajectories.Rmd
FunctionalGraph

The taxonomic diversity was assessed through Richness and the Hill number translation of Shannon and Simpson indices [@Hill1973]. 
>>To tackle the unequal number of recruited trees among treatments the indices bias corrected estimator were used, following [@Chao2015;@Marcon2015b].

@@

```{r NMDSplans, out.width = '100%', fig.asp = 1.2/2, echo=FALSE, fig.cap="Trajectories of the plots in terms of (ref:Bolda) flora composition and (ref:Boldb) functional composition regarding the 6 leaf and stem functional traits,the maximum allometric height and seed mass class in the two-dimensional space from the NMDS performed for the 30 years after disturbance. Distance matrix for NMDS were computed from the Bray-curtis dissimilarity between successive inventories. Line colors represent the disturbance treatment (green for control, blue for T1,orange for T2 and red for T3).", fig.env="figure*"}
load("DB/FunctionalComposition_forGraph")
load("DB/TaxoComposition_forGraphs")

@@

The functional diversity trajectories of plots based on the 8 leaf, stem and life history traits was examined through the Rao diversity.
For all undisturbed plots the functional diversity remained comparable to the reference values 5 years after disturbance (1989 inventories).
For all disturbed plots the functional trajectories followed a unimodal trajectory with a maximum positively correlated to disturbance intensity ($\rho_{spearman}=XX$) (Figure \@ref(fig:DivFun)). 
The plot 7 from treatment 1 that displayed a constantly outlying diversity was removed from the graphical representation for better readability, see appendix for full graph.
Thirty years after disturbance all plots, whenever the initial disturbance intensity, regained diversity values similar to their initial avule and to those of control plots.

```{r DivFun, out.width = '80%', echo=FALSE, fig.cap="Trajectories of the Rao functional diversity over 30 years after disturbance. Trajectories correspond to the median (solid line) and 0.025 and 0.975 percentile (gray envelope) observed after 50 iteration of the taxonomic uncertainty propagation. Initial treatments are represented by solid lines colorswith green for control, blue for T1,orange for T2 and red for T3.and the missing trait value filling processes.", fig.env="figure*"}
load("DB/FunctionalTraj_ForGraphsnew")

FunTraj(CompleteFun,remove=F)

>>>>

The taxonomic diversity was assessed through Richness and the Hill number translation of Shannon and Simpson indices [@Hill1973].

@@

```{r NMDSplans, out.width = '100%', fig.asp = 1.2/2, echo=FALSE, fig.cap="Trajectories of the plots in terms of (ref:Bolda) flora composition and (ref:Boldb) functional composition regarding the 6 leaf and stem functional traits,the maximum allometric height and seed mass class in the two-dimensional space from the NMDS performed for the 30 years after disturbance. Distance matrix for NMDS were computed from the Bray-curtis dissimilarity between successive inventories. Line colors represent the disturbance treatment (green for control, blue for T1,orange for T2 and red for T3).", fig.env="figure"}
load("DB/FunctionalComposition_forGraph")
load("DB/TaxoComposition_forGraphs")

@@

The functional diversity trajectories of plots based on the 8 leaf, stem and life history traits was examined through the Rao diversity.
For all undisturbed plots the functional diversity remained comparable to the reference values 5 years after disturbance (1989 inventories).
For all disturbed plots the functional trajectories followed a unimodal trajectory with a maximum positively correlated to disturbance intensity ($\rho_{spearman}=0.73$) (Figure \@ref(fig:DivFun)). 
The plot 7 from treatment 1 that displayed a constantly outlying diversity was removed from the graphical representation for better readability, see appendix for full graph.
Thirty years after disturbance all plots, whenever the initial disturbance intensity, regained diversity values similar to their initial avule and to those of control plots.

```{r DivFun, out.width = '100%', echo=FALSE, fig.cap="Trajectories of the Rao functional diversity over 30 years after disturbance. Trajectories correspond to the median (solid line) and 0.025 and 0.975 percentile (gray envelope) observed after 50 iteration of the taxonomic uncertainty propagation. Initial treatments are represented by solid lines colorswith green for control, blue for T1,orange for T2 and red for T3.and the missing trait value filling processes.", fig.env="figure"}
load("DB/FunctionalTraj_ForGraphs")

FunTraj(CompleteFun,remove=T)
